---
title       : Analyzing mtcars database.
subtitle    : Simple regression models using mtcars database.
author      : Borja Santos Zorrozua.
job         : Phd student. University of The Basque Country (UPV/EHU)
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction:
This presentation has been done to explain the shiny application. As the title says, I've used the mtcars database which is implemented in the datasets library.
```{r}
library(datasets)
packageDescription("datasets")
```

---

## Description
### mt cars dataset: 
This dataset was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models). 
### Citation:
Henderson and Velleman (1981), Building multiple regression models interactively. *Biometrics*, **37**, 391-411.

### Note:
Some discrete variables were considered continuous. To fix this problem, these variables were coerced to be factor variables in order to perform better regression models: cyl, vs, am, gear and carb. So I had to build new dataset to include the correct type of these variables, and I called it database.
```{r,echo=FALSE}
database <- mtcars
database$cyl <- as.factor(database$cyl)
database$vs <- as.factor(database$vs)
database$am <- as.factor(database$am)
database$gear <- as.factor(database$gear)
database$carb <- as.factor(database$carb)
```

---

## Database summary
The structure of the variables in the final dataset is
```{r}
str(database)
```

---

## Main code of the server.R file
```{r,eval=FALSE}
# Compute the forumla text in a reactive expression since it is 
# shared by the output$caption and output$mpgPlot expressions
  formulaText <- reactive({
    paste("mpg ~", input$id1)
  })
  # Return the formula text for printing as a caption
  output$caption <- renderText({
    formulaText()
  })
  # Generate plots of the requested variable against mpg
  output$mpg_model <- renderPrint(summary(lm(as.formula(formulaText()))))
  output$mpgPlot <- renderPlot({
    plot(as.formula(formulaText()), 
            data = database,ylab="Miles per Gallon",main=formulaText(),col="red",pch=16)
  })
  output$diagnostic1 <- renderPlot(plot(lm(as.formula(formulaText())),which=1,col="blue",pch=16))
  output$diagnostic2 <- renderPlot(plot(lm(as.formula(formulaText())),which=2,col="blue",pch=16))
```

